Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-08 writeup/rocha_etal.tex
Fix legend
Fixes typo.

The inertia-gravity waves significantly project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged SSH in October (Figure \ref{4}b): at scales smaller than 100 km, the spectra
of hourly SSH roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
SSH roughly follows a $-5$ power-law. At these scales, 33$\%$ of the SSH variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October! Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface inertia-gravity waves conspire to yield very weak seasonality
in the spectra of KE and SSH variance based on hourly fields.

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_3.pdf}
  \caption{A comparison between spectra of the two LLC simulations 1/24$^\circ$
  (green) and 1/48$^\circ$ (purple). The statistical errorbars represent conservative
  significance levels considering that there are only four independent relations
  for the monthly spectra.}
  \label{figS2_3}
  \end{center}
\end{figure*}

>>>>

The inertia-gravity waves project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged SSH in October (Figure \ref{fig4}b): at scales smaller than 100 km, the spectra
of hourly SSH roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
SSH roughly follows a $-5$ power-law. At these scales, 33$\%$ of the SSH variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October! Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface inertia-gravity waves conspire to yield very weak seasonality
in the spectra of KE and SSH variance based on hourly fields.

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_3.pdf}
  \caption{A comparison between spectra of the two LLC simulations 1/24$^\circ$
  (green) and 1/48$^\circ$ (purple). The statistical errorbars represent conservative
  95$\%$ significance levels.}
  \label{figS2_3}
  \end{center}
\end{figure*}
